Many Analystis Project

### 2022-03-12 History/analysis-religious-only.Rmd
order files
create history foldrer

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggraph")
library("lme4")
library("table1")
library("ggeffects")
library("kableExtra")
library("naniar") # missingness
library("Amelia")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

>>>>

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

### 2022-03-12 History/analysis-v-2.Rmd
order files
create history foldrer

dag1 <- image_ggplot(image_read(here::here("figs","dg_1.tiff")),
                     interpolate = T)
dag1
dag2 <- image_ggplot(image_read(here::here("figs","dg_2.tiff")), interpolate = T)
dag2
dag3 <- image_ggplot(image_read(here::here("figs","dg_3.tiff")), interpolate = T)
dag3
dag4 <- image_ggplot(image_read(here::here("figs","dg_4.tiff")),
                     interpolate = T)
dag4
library(patchwork)
daggraph <- dag1 + dag4 + dag3  / ( dag2) + 
  plot_annotation(title = "Directed Acyclic Graphs (DAGs) clarify assumptions and hazards for causal identification", tag_levels = "a")

>>>>

dag1 <- image_ggplot(image_read(here::here("figs","dg_1.tiff")),
                     interpolate = T)
dag1
dag2 <- image_ggplot(image_read(here::here("figs","dg_2.tiff")), interpolate = T)
dag2
dag3 <- image_ggplot(image_read(here::here("figs","dag_3.tiff")), interpolate = T)
dag3
dag4 <- image_ggplot(image_read(here::here("figs","dg_4.tiff")),
                     interpolate = T)
dag4
library(patchwork)
daggraph <- dag1 + dag4 + dag3  / ( dag2) + 
  plot_annotation(title = "Directed Acyclic Graphs (DAGs) clarify assumptions and hazards for causal identification", tag_levels = "a")
